%-------------------------
% Resume in Latex
% Author : Roop Sai Charan
%------------------------

\documentclass[letterpaper,9pt]{extarticle}

% Set font to Times New Roman
\usepackage{mathptmx} 

\usepackage{latexsym}
% Using the geometry package for safe, tight margins. This prevents the blank first page.
\usepackage[margin=0.4in]{geometry} 
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Safer section spacing to prevent title overlaps
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{1pt}\item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & #2 \\ 
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-6pt}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, topsep=2pt, itemsep=1pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Roop Sai Charan Kothamasu} \\ \vspace{2pt}
    \small
    +1-352-721-6208 $|$
    \href{mailto:roopsai2003@gmail.com}{roopsai2003@gmail.com} $|$
    \href{https://github.com/Roopsaicharan}{github.com/Roopsaicharan} $|$
    \href{https://www.linkedin.com/in/roop-sai-charan-kothamasu-85062b24b/}{linkedin.com/in/roop-sai-charan-kothamasu}
\end{center}

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Florida}{Gainesville, FL}
      {Master of Science in Computer Science}{Aug 2025 -- Aug 2027}
    \resumeSubheading
      {SRM University}{Andhra Pradesh, India}
      {Bachelor of Technology in Computer Science}{Mar 2021 -- Mar 2025}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{TECHNICAL SKILLS}
 \vspace{2pt}
  \begin{itemize}[leftmargin=0.15in, label={}, nosep]
    \small{\item{
      \textbf{Languages:} Python, JavaScript, Java, C, C++, SQL, Solidity \\
      \textbf{AI \& Machine Learning:} Generative AI (LLMs, RAG), LangChain, OpenAI API, TensorFlow, PyTorch, Hugging Face, Scikit-learn \\
      \textbf{Front-end Technologies:} React.js, Next.js, HTML5, CSS3, Tailwind CSS, Bootstrap \\
      \textbf{Back-end Technologies:} Node.js, Express.js, REST APIs, MongoDB, PostgreSQL, Pinecone (Vector DB) \\
      \textbf{Cloud and DevOps:} AWS (EC2, CloudWatch, S3), CI/CD, Docker, Git, Linux/UNIX \\
      \textbf{Data Science Tools:} Pandas, NumPy, Matplotlib, OpenCV, Jupyter Notebook \\
      \textbf{Development Tools:} GitHub, VS Code, Google Colab, Postman, Agile/Scrum
    }}
  \end{itemize}
 \vspace{-4pt}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Self-Study under Ivan Ruchikin}{Remote}
      {Autonomous Vehicle Systems Research}{2023 -- Present}
      \resumeItemListStart
        \resumeItem{Conducted comprehensive self-directed research on autonomous vehicle systems under the mentorship of Ivan Ruchikin.}
        \resumeItem{Explored advanced concepts in self-driving technologies, focusing on sensor fusion, path planning, and autonomous navigation control systems.}
        \resumeItem{Analyzed state-of-the-art algorithms for autonomous vehicles to understand their practical implementations and safety critical aspects in real-world environments.}
      \resumeItemListEnd

    \resumeSubheading
      {SRM University AP}{Andhra Pradesh, India}
      {Special Project Intern -- Blockchain Research}{Dec 2024 -- Mar 2025}
      \resumeItemListStart
        \resumeItem{Designed and deployed Solidity smart contracts on Ethereum for tamper-proof patient data storage, integrating Node.js REST APIs and MongoDB for off-chain data management across 500+ simulated users.}
        \resumeItem{Implemented JWT-based role access control for 3 distinct user roles, eliminating unauthorized access entirely and ensuring 99.9\% data integrity throughout the system.}
        \resumeItem{Collaborated directly with supervising professor to iterate on system architecture, rapidly adapting to blockchain concepts and delivering a fully functional prototype within a 3-month timeline, contributing to an ongoing publication and patent filing.}
      \resumeItemListEnd

    \resumeSubheading
      {APSSDC}{Remote}
      {AWS Cloud Computing Intern}{Jun 2023 -- Aug 2023}
      \resumeItemListStart
        \resumeItem{Launched scalable web applications on AWS EC2 with automated monitoring, improving system uptime by 55\% and reducing downtime incidents by 40\%.}
        \resumeItem{Engineered CI/CD pipelines using AWS CodePipeline and GitHub Actions, reducing manual deployment time by 70\% and accelerating release cycles from 5 days to 1.5 days.}
        \resumeItem{Optimized resource allocation across 12+ EC2 instances using CloudWatch analytics, decreasing infrastructure costs by 25\% while maintaining 99.9\% availability.}
      \resumeItemListEnd

    \resumeSubheading
      {SRM University AP}{Andhra Pradesh, India}
      {Machine Learning Research Intern}{Jan 2022 -- Mar 2022}
      \resumeItemListStart
        \resumeItem{Developed end-to-end ML pipelines processing 15,000+ records with 95\% accuracy using Python, Pandas, and Scikit-learn.}
        \resumeItem{Implemented ensemble learning techniques (Random Forest, XGBoost) improving prediction stability by 85\% and F1-score from 0.72 to 0.89.}
        \resumeItem{Conducted model evaluation using cross-validation, achieving ROC-AUC of 0.92+ across 6 different ML algorithms.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
  \resumeSubHeadingListStart
    \resumeProjectHeading{\textbf{MeetMint: AI-Powered Productivity Dashboard} $|$ \emph{Go, React, Gemini 1.5 Flash, RAG, SQLite}}{ March 2026 -- May 2026}
      \resumeItemListStart
        \resumeItem{Architected a full-stack AI dashboard using Go and React to transform meeting audio into structured project metadata, leveraging Gemini 1.5 Flash for low-latency transcription analysis and task extraction.}
        \resumeItem{Engineered a local Retrieval-Augmented Generation (RAG) pipeline using SQLite and embeddings, enabling context-aware Q\&A over meeting history with support for manual transcript refinement.}
        \resumeItem{Developed a premium Glassmorphism UI with Framer Motion and secure multimedia BLOB storage, maintaining a robust test suite of 35+ backend and integration tests.}
      \resumeItemListEnd

    \resumeProjectHeading{\textbf{Decentralized Patient Record Management System} $|$ \emph{Node.js, MongoDB, Solidity, Ethereum}}{Dec 2024 -- Mar 2025}
      \resumeItemListStart
        \resumeItem{Architected blockchain-based healthcare platform using Solidity smart contracts and Node.js REST APIs, enabling secure management for 500+ simulated users with 99.9\% data integrity.}
        \resumeItem{Enforced granular permission management across doctor, patient, and admin roles using JWT authentication, achieving full compliance with healthcare data privacy standards.}
        \resumeItem{Released Ethereum smart contracts with audit logging, decreasing manual verification by 40\% through immutable transaction records.}
      \resumeItemListEnd

    \resumeProjectHeading{\textbf{AI-Powered Game Room Chatbot} $|$ \emph{Python, LangChain, OpenAI API, Hugging Face, Pinecone}}{May 2026 -- Jul 2026}
      \resumeItemListStart
        \resumeItem{Designed and deployed an intelligent Discord chatbot utilizing Python and LangChain to provide context-aware gaming assistance and dynamic community engagement.}
        \resumeItem{Integrated OpenAI API and Hugging Face transformers for advanced Natural Language Processing, enabling real-time chat moderation, toxicity filtering, and conversational interactions.}
        \resumeItem{Engineered a Retrieval-Augmented Generation (RAG) pipeline using Pinecone vector database to instantly retrieve game stats, lore, and personalized player recommendations, boosting daily user engagement.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{PUBLICATIONS}
  \resumeSubHeadingListStart
    \resumeItem{R.S. Charan et al. (2024). \href{https://doi.org/10.1109/ICEEICT61591.2024.10718516}{\textit{Analyzing Lossless Image Compression Techniques for IoT Devices}}, ICEEICT 2024.}
    \resumeItem{R.S. Charan et al. (2024). \href{https://doi.org/10.1109/ICAECT63952.2025.10958911}{\textit{An Explainable AI Driven Hybrid Model for Enhanced Intrusion Detection in Network Security}}.}
    \resumeItem{R.S. Charan et al. (2024). \textit{Decentralized Patient Record Management System} --- Publication and patent under process.}
  \resumeSubHeadingListEnd

\end{document}
